Community-Conditioned Language Models

### 2020-10-27 paper/paper.tex
add Data sets section

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

\section{Experimental setup}
\subsection{Data Sets}
\subsection{Models}
\subsection{Training scheme}

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

\section{Experimental setup}
\subsection{Data Sets}

To investigate variation across communities, we use comments collected 
from the social media website Reddit.\footnote{Comments were obtained 
from the archive at \href{https://pushshift.io/}{pushshift.io} \cite{Baumgartner2020}.}

Reddit is divided into forums called \textit{subreddits}, 
which are typically organized around a topic of interest. 
Our dataset includes comments from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} comments per month for each month 
in the three years between 2015 and 2017.\footnote{
We initially selected \num{50} subreddits, 
but excluded four from further analysis: 
two which were primarily non-English and two with particularly short average comment lengths.}
Each community corpus consist of \num{50000} randomly selected comments from the year 2015.

Comments were preprocessed as follows: 
We removed markdown formatting, extracting only rendered text. 
We exclude the content of block quotes, code blocks, and tables. 
We tokenized the comments using the default English model for the SpaCy tokenizer,\footnote{Version 2.2.3}
and lower-cased all tokens.

\subsection{Models}
\subsection{Training scheme}

@@

\bibliography{paper}
\bibliographystyle{acl_natbib}
